
This file goes through the scoring for the BAM project -- PRIOR to switching over to the 'scheduled' redcap in Fall 2022. There is a separate scoring file for that project (Fall 2022 and later) which tweaks some changes related to the scheduled version of the project and then combines the new incoming data from that Redcap project with this data. 

# 0. Load packages
```{r, message=FALSE}
library(readxl)
library(haven)
library(cgwtools)
library(scorekeeper)
library(purrr)
library(tibble)
library(dplyr)
library(lubridate)
library(anytime)
library(tidyr)
library(Hmisc)
library(stringr)
```

The current scoring completes redcap scoring for the BAM project on data from 2020-Spring 2022; prior to switching over to the 'scheduled' BAM module

## Load Data
```{r}
# Load Raw data; name cleaned data file for output
data <- read.csv('data/BAMBodyAdvocacyMovem_DATA_2022-10-22_1637.csv')  %>% 
  filter(redcap_event_name != 'consent_form_arm_1')
```

## Clean known data issues

# 2. Scorekeep 

```{r, warning=FALSE}

# Load Individual Scoresheets
filenames <- list.files('scoresheets1_clean/') # MAKE SURE THIS IS THE CORRECT DIRECTORY NAME
filenames <- paste('scoresheets1_clean', filenames, sep = '/' )
ldf <- lapply(filenames, read_xlsx)

# List of Measure Names from the Scoresheets
measures <- list.files('scoresheets1_clean/') 
measures <- gsub('.xlsx*', '', measures)

# Names the scoresheets
names(ldf) <- measures

# Cleans and saves cleaned data for each measure 

x <- vector(mode = 'list', length = (length(measures)))
names(x) <- measures

tibble_func_1 <- function(x) {
  y = as_tibble(x)
  return (y) }

cleaned_data <- purrr::map(x, tibble_func_1)

for (i in 1:length(measures)) {
cleaned <- scorekeep(data, ldf[[i]])
cleaned_last <- cleaned[[max(ldf[[i]]$step)]]
cleaned_data[[i]] <-cleaned_last
}
```

# 3. Post-Scorekeep Data Processing

## Demographics
```{r}
DCF <- data %>%
    select(record_id, redcap_event_name, sex_orientation, specify_sex_orientation, starts_with('dcf')) |> 
    filter (dcf_date > '2019-01-01') |> 
    mutate(
    dcf_date = anydate(dcf_date), #convert dcf_date to date type variable
    dcf_birthday = anydate(dcf_age), #convert dcf_age to date type variable and save as birthday
    dcf_age = (as.numeric(dcf_date - dcf_birthday))/365.25) %>% #calculate age in years  
  rename(Race_White = dcf_race___1, Race_AA_Black = dcf_race___2 , Race_Asian = dcf_race___3, Race_NativeAmerican = dcf_race___4, Race_Hispanic_Latino = dcf_race___5, Race_Pacific_Island = dcf_race___6, Race_other = dcf_race___7)  
DCF <- DCF |> 
  mutate (sex_orientation = labelled(DCF$sex_orientation, c('Heterosexual' = 1, 'Gay/Lesbian' = 2, 'Bisexual' = 3, 'Other' = 4))) |> 
  mutate (dcf_gender = recode (dcf_gender, `1` = 0, `2` = 1, `3` = 2), 
          dcf_gender = labelled(DCF$dcf_gender, c('Male' = 0, 'Female' = 1, 'Nonbinary' = 2))) |>   mutate(race_nonwhite = rowSums(across(c(Race_AA_Black:Race_other)))) |> 
  mutate(Race_nonwhite = case_when(race_nonwhite>0 ~1,
                                   race_nonwhite==0~ 0)) |> 
  mutate(Race_Mixed = rowSums(across(c(Race_White:Race_other))))|> 
  mutate(Race_Mixed = case_when(Race_Mixed > 1 ~1,
                                Race_Mixed <=1 ~ 0)) |> 
  mutate(Race = case_when(Race_Mixed == 1 ~ 5,
                          Race_AA_Black == 1 & Race_Mixed == 0 ~ 4,
                          Race_NativeAmerican == 1 & Race_Mixed == 0~ 3,
                          Race_Hispanic_Latino == 1 & Race_Mixed == 0 ~ 2,
                          Race_Asian == 1 & Race_Mixed == 0 ~ 1,
                          Race_Pacific_Island == 1 & Race_Mixed == 0 ~ 1, 
                          Race_White == 1 & Race_Mixed == 0 ~ 0,
                          )) 
DCF$dcf_age[[19]] <- NA #person did not write appropriate age

DCF <- DCF |> 
  mutate(Race = labelled(DCF$Race, c('White' = 0, 'AAPI' = 1, 'Hispanic/Latino' = 2, 'Native American' = 3, 'Black' = 4, 'Mixed Race' = 5))) |> 
rename(timepoint = 'redcap_event_name') |> 
rename(id = 'record_id') %>% 
  select(id, dcf_date,timepoint, dcf_age, dcf_student, sex_orientation, dcf_gender, dcf_gender_other, dcf_working, dcf_living,Race, Race_nonwhite, Race_White:Race_other)

label(DCF$dcf_age)="date of assessment minus birthday"
label(DCF$sex_orientation)="With which sexual orientation do you primarily identify?"
label(DCF$dcf_gender)="Gender"
label(DCF$dcf_date)="date of assessment"
label(DCF$dcf_student)="Are you a student?"
label(DCF$dcf_working)="Are you currently working?"
label(DCF$dcf_living)="Where are you living/staying right now?"

```

## 3.1. Weight Suppression Variables
```{r}
weight_vars <- data %>%
  select(record_id, starts_with('wdqhq'), starts_with('wdwq'), starts_with('dcf_weight'), dcf_height) %>% 
#filter by wdwq_complete that is not null
  filter (!(is.na(wdwq_complete))) %>% 
#remove "Test" record ID
  filter (!(record_id == "Test"),
          wdwq_complete == 2)

#Current Weight
WT_VARS <- weight_vars %>% 
  mutate (wdhq_current_wt = as.numeric(wdqhq_pounds)) %>% 
  select (record_id, wdhq_current_wt, wdqhq_pounds, wdqhq_weight_lbs_kg, wdqhq_q, wdqhq_leastpounds) %>% 
  mutate (dwhq_wt_kg_current = case_when(wdqhq_weight_lbs_kg == 2 ~ as.numeric(wdhq_current_wt),
                                 wdqhq_weight_lbs_kg == 1 ~ as.numeric(wdhq_current_wt*.4536))) %>% 
  mutate (dwhq_wt_kg_high = case_when(wdqhq_weight_lbs_kg == 2 ~ as.numeric(wdqhq_q),
                                 wdqhq_weight_lbs_kg == 1 ~ as.numeric(wdqhq_q*.4536))) %>%  
  mutate (dwhq_wt_kg_low = case_when(wdqhq_weight_lbs_kg == 2 ~ as.numeric(wdqhq_leastpounds),
                                 wdqhq_weight_lbs_kg == 1 ~ as.numeric(wdqhq_leastpounds*.4536))) %>% 
  mutate (dwhq_wt_suppress_current_kg = dwhq_wt_kg_high -dwhq_wt_kg_current) %>% 
    mutate (dqhq_wt_suppress_current_kg = ifelse(dwhq_wt_suppress_current_kg<0, 0, dwhq_wt_suppress_current_kg)) %>% 
  mutate (dwhq_wt_suppress_current_lbs = round(dwhq_wt_suppress_current_kg*2.205, 1)) %>% 

  select(record_id, dwhq_wt_kg_low, dwhq_wt_kg_current, dwhq_wt_kg_high, dwhq_wt_suppress_current_kg, dwhq_wt_suppress_current_lbs)


#Height
height <- weight_vars %>% 
  select (record_id, wdqhq_height, wdqhq_height_feet_in_cm) %>% 
  separate (wdqhq_height, into = c("feet", "inches"), "foot|'|ft|\\.") %>% 
  mutate(inches = str_extract(inches, "[[:digit:]]"))

height$inches[[5]] <- 0
height <- height %>% 
  mutate(dwhq_height_cm = case_when(wdqhq_height_feet_in_cm == 2 ~ as.numeric (feet),
                               wdqhq_height_feet_in_cm == 1 ~ (as.numeric (feet)*12 + as.numeric(inches))*2.54)) 

height <- height %>% 
  select(record_id, dwhq_height_cm)

WT_VARS <- left_join(WT_VARS, height) %>% 
  rename(id = 'record_id') %>% 
  mutate(dwhq_bmi_current = dwhq_wt_kg_current/(dwhq_height_cm^2)*10000) %>% 
  mutate(dwhq_bmi_low = dwhq_wt_kg_low/(dwhq_height_cm^2)*10000) %>% 
  mutate(dwhq_bmi_high = dwhq_wt_kg_high/(dwhq_height_cm^2)*10000) %>% 
  mutate(dwhq_bmi_suppress_current = dwhq_bmi_high-dwhq_bmi_low) %>% 
  mutate(timepoint = 'questionnaires_arm_2')

```
## Randomization

```{r}
Group <- read_xlsx('data/BAM_Randomization.2020-2022.xlsx') 
```


# 4. Long Dataset

```{r}

cleaned_data <- cleaned_data %>% 
  append(list(Group)) %>% 
  append(list(DCF)) %>% 
  append(list(WT_VARS)) 

names(cleaned_data)[[length(cleaned_data)-2]] <- 'Group'
names(cleaned_data)[[length(cleaned_data)-1]] <- 'DCF'
names(cleaned_data)[[length(cleaned_data)]] <- 'WT_VARS'

long_data <- cleaned_data[[1]]

j = 2
while (j <= length(cleaned_data)) {
  long_data <- full_join(long_data, cleaned_data[[j]])
  j = j+1
}


long_data <- long_data %>% 
 mutate(timepoint = recode(timepoint, questionnaires_arm_2 = 'baseline', questionnaires_arm_3 = 'post', questionnaires_arm_4 = '8wk')) %>% 
  filter(timepoint != 'consent_form_arm_1')

```
# 5. Wide Dataset

```{r}
cols <- colnames(long_data)
cols <- cols[-c(1,2)]

wide_data <- long_data %>% 
  tidyr::pivot_wider(names_from = timepoint, 
                     values_from = cols) %>% 
  janitor::remove_empty("cols")
```


# 6. Save cleaned data 
```{r}
# Dataset with dataframes separated by measure
BAM1_redcap <- cleaned_data 
save(BAM1_redcap, file = 'data/BAM1_redcap.RData') 


# Long Dataframe
BAM1_redcap_long <- long_data
save(BAM1_redcap_long, file = 'data/BAM1_redcap_long.RData') 

# Wide Dataframe
BAM1_redcap_wide <- wide_data
save(BAM1_redcap_wide, file = 'data/BAM1_redcap_wide.RData') 
```

# 7. Clear environment and load data for checking
```{r}
rm(list = ls())
load('data/BAM1_redcap.RData')
load('data/BAM1_redcap_long.RData')
load('data/BAM1_redcap_wide.RData')

```

