---
title: "Beck Depression Inventory-II"
output: html_document
date: '2022-10-02'
---
## Background
The Beck Depression Inventory-II (BDI-II) developed in 1996, was derived from the BDI. The 21-item self-administered survey is scored on a scale of 0–3 in a list of four statements arranged in increasing severity about a particular symptom of depression. Total score of 0–13 is considered minimal range, 14–19 is mild, 20–28 is moderate, and 29–63 is severe.

References:
[Beck AT, Steer RA, Brown GK. Manual for The Beck Depression Inventory Second Edition (BDI-II). San Antonio: Psychological Corporation; 1996.]

[Beck AT, Steer RA, Ball R, Ranieri W. Comparison of Beck Depression]

## Scoresheet
To clean the data, the scoresheet:

(1) selects only variables that are relevant for the current measure

(2) recoded all necessary variables (e.g. changing " I sleep somewhat less than usual=1b" to " I sleep somewhat less than usual=1")

(3) Creates a symptom total score, which gives total count of the number of symptoms (0-3) that are present for each individual

## Key Variables
'bdi_sum' (defines the sum of symptoms)

```{r}
library(haven)
library(cgwtools)
library(scorekeeper)
library(readxl)
```

```{r}
BAM_RA_raw <- read.csv("BAM_RA_raw.csv")
BDI_scoresheet <- read_excel("BDI_scoresheet.xlsx")
cleaned_data <- scorekeep(BAM_RA_raw, BDI_scoresheet)
```

